Extended Formal Analysis of the EDHOC Protocol in Tamarin

### 2022-07-22 intro.tex
[add] citation to correct spec in introduction

%-------------------------------------------------------------------------- sub
\subsection{Contributions}
\label{sec:contributions}
In this paper, we extend the work presented in~\cite{Norr21}.
%
We analyze the version of \mEdhoc{} as in~\cite{}.
%
We extend the adversary model and \mTamarin{} system models to capture weak
post-compromise security (PCS) and model Trusted Execution Environments
(TEE).
%
We check for the following properties:
\begin{itemize}
\item Injective agreement
\item Implicit agreement
\item Weak post-compromise security for the session-key material
\item Perfect Forward Secrecy (PFS) for the session-key material
\item Secrecy and integrity of \mADthree
\end{itemize}
%
We follow the definition of weak PCS by~\cite{DBLP:conf/csfw/Cohn-GordonCG16},
which subsumes PFS.
%
We also discuss various issues arising in relation to the use of trusted
execution environments (TEEs), denial of service (DoS) attacks, error handling,
the negotiation of parameters (which the formal model abstracts
away) for establishing the protocol, and other potential attacks and concerns.
%
We have communicated these issues to the developers of the protocol.
%

>>>>

%-------------------------------------------------------------------------- sub
\subsection{Contributions}
\label{sec:contributions}
In this paper, we extend the work presented in~\cite{Norr21}.
%
We formally analyze the version of \mEdhoc{} as in~\cite{}.
%
We formally analyze the \mEdhoc{} specification as of July
2020~\cite{our-analysis-selander-lake-edhoc-00}.
%
Out formal analysis applies to v5 of the \mSpec{} (February 2021).
%
However, we do refer to various aspects
(error handling, denial of service etc) of this latest version,
in Sections~\ref{sec:errorHandling} and \ref{sec:discussion}.
We extend the adversary model and \mTamarin{} system models to capture weak
post-compromise security (PCS) and model Trusted Execution Environments
(TEE).
%
We formally verify the following properties:
\begin{itemize}
\item Injective agreement
\item Implicit agreement
\item Weak post-compromise security for the session-key material
\item Perfect Forward Secrecy (PFS) for the session-key material
\item Secrecy and integrity of \mADthree
\end{itemize}
%
We follow the definition of weak PCS by~\cite{DBLP:conf/csfw/Cohn-GordonCG16},
which subsumes PFS.
%
We also discuss various issues arising in relation to the use of trusted
execution environments (TEEs), denial of service (DoS) attacks, error handling,
the negotiation of parameters (which the formal model abstracts
away) for establishing the protocol, and other potential attacks and concerns.
%
We have communicated these issues to the developers of the protocol.
%
